---
title: "project 1"
author: "Yuyao Wang yw3395"
date: "2/2/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(tm)
library(purrr)
library(tibble)
library(textdata)
library(data.table)
library(tidytext)
library(tidyverse)
library(DT)
library(vcd)
library(rstan)
library(dplyr)
library(stringr)
library(wordcloud2)
library(gridExtra)
library(ggplot2)
library(ngram)
library(tidyr)
library(PerformanceAnalytics)
library(stringr)
library(wordcloud2)
library(RColorBrewer)
library(wordcloud)
library(reshape2)
library(scales)

```{r include=FALSE}
library(tm)
library(purrr)
library(tibble)
library(textdata)
library(data.table)
library(tidytext)
library(tidyverse)
library(DT)
library(vcd)
library(rstan)
library(dplyr)
library(stringr)
library(wordcloud2)
library(gridExtra)
library(ggplot2)
library(ngram)
library(tidyr)
library(PerformanceAnalytics)
library(stringr)
library(wordcloud2)
library(RColorBrewer)
library(wordcloud)
library(reshape2)
library(scales)
```

```{r warning=FALSE}
load("../output/processed_lyrics.RData")
```

```{r warning=FALSE}
corpus1<- VCorpus(VectorSource(dt_lyrics$lyrics))
#create a tidy data structure
word_text<- tidy(corpus1) %>%
  select(id,text)
#break the text into individual tokens
word_df=word_text%>%
  unnest_tokens(word, text)%>%
  as_tibble()
```

###Preliminary word frequency analysis


We first perform a word frequency analysis on the lyrics. But it turned out that it didn't make much sense. Because common words are some particle or prepositions, conjunctions, etc., such as the, am, and etc. This will be described in detail below.

To be specific, first, we create word frequency matrix a nd view high frequency vocabulary.

```{r}
frequencies <- DocumentTermMatrix(corpus1)
frequencies
```

```{r eval=FALSE}
findFreqTerms(frequencies, lowfreq=20000) 
# lowfre = 20000 means the terms that appear at least 20000 times
```


It can be seen that there are 125704 observations and 286988 words in the equivalence.

Also, we found that "'cause","about"，“again","ain't","all","alone","always","i'll","i'm",
"i've","inside","into", "it","it's...these words have appeared more than 20000 times in total. 
Create visualizations of the most common words.We found that almost all of these high-frequency words are prepositions or particle parts, which have nothing to do with emotion.

```{r warning=FALSE}
word_df%>%
  count(word, sort = TRUE) %>%
  filter(n > 100000) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill=word)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

Check the word frequency of the lyrics

```{r warning=FALSE}
dt_lyrics=dt_lyrics%>%
  mutate(id=as.character(id))
word_df2<- tidy(corpus1) %>%
  left_join(dt_lyrics,by="id")%>%
  select(text,genre) %>%
  mutate(id = row_number()) %>% 
  unnest_tokens(word, text)

frequency <- word_df2%>% 
  group_by(genre) %>% 
  count(word, sort = TRUE) %>% 
  left_join(word_df2%>% 
              group_by(genre) %>% 
              summarise(total = n())) %>%
  mutate(freq = n/total)%>%
  select(genre,word,freq)%>%
  pivot_wider(id_cols=word, names_from = "genre", values_from = "freq")
frequency
```

We can compare the frequency of lyrics in different genres by simply drawing a picture.
However, since the frequency of occurrence is prepositions or conjunctions, such as the, and, it, etc., this comparison is actually meaningless when the data is very large.

```{r warning=FALSE}
ggplot(frequency, aes(Metal,Rock)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")
```

###Text sentiment analysis


Because songs are an important way for people to express their emotions, the melody and lyrics of the songs are infiltrated with different emotions.
Thus, next we will analyze it from the perspective of emotions. Observing different types of music, commonly expressing emotions (positive and negative).
We first use a dictionary to distinguish between these words. (Positive or negative)

there are a variety of methods and dictionaries that exist for evaluating the opinion or emotion in text. The tidytext package contains several sentiment lexicons. Three general-purpose lexicons are AFINN from Finn Årup Nielsen, bing from Bing Liu and collaborators, and nrc from Saif Mohammad and Peter Turney. All three of these lexicons are based on unigrams, i.e., single words.

Firstly, I use bing lexicon to get the dictionary and then match the words with our dataset.


###1.the frequency of expressing emotional words

```{r}
bing_pos<-get_sentiments("bing") %>% 
  filter(sentiment=="positive")
bing_neg<-get_sentiments("bing") %>% 
  filter(sentiment=="negative")

count_pos<-word_df%>% 
  inner_join(bing_pos,by = "word") %>% 
  count(word)
count_neg<-word_df%>% 
  inner_join(bing_neg,by = "word") %>% 
  count(word)

bing_word_counts <-word_df%>%
  inner_join(get_sentiments("bing"),by = "word") %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
bing_word_counts

```

We found that love, like, right, good, and well are the most frequent positive affective words, especially love and like. Both of them appear in the database 150,000 times. And hard, fall, lost, wrong are the positive emotion words with the lowest frequency. For a more intuitive presentation, we visualize it. 

```{r warning=FALSE}
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

Using the wordcloud, we draw the words with the most occurrences of positive and negative words. The larger the shape of the word, the more times it appears.

```{r warning=FALSE}
wordcloud_pos<-word_df%>%  
  inner_join(bing_pos,by = "word") %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))

wordcloud_neg<-word_df%>%  
  inner_join(bing_neg,by = "word") %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))

wordcloud_both<-word_df%>%  
  inner_join(get_sentiments("bing"),by = "word") %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 200)
```

###2. the word strength of positive and negative emotions in different songs

Next, we divide according to different genresm and compare sentiments among different genre.It’s worth looking deeper to understand why some genre ended up more positive or negative than others. For that, we can examine the total positive and negative contributions among each genre.

```{r warning=FALSE}
wordsentiment_pos_genre<-word_df2%>%  
  inner_join(bing_pos,by = "word") %>%
  group_by(genre)%>%
  count(word) %>%
  ungroup()

wordsentiment_neg_genre<-word_df2%>%  
  inner_join(bing_neg,by = "word") %>%
  group_by(genre)%>%
  count(word) %>%
  ungroup()

sumsentiment_neg_genre=wordsentiment_neg_genre%>%
  group_by(genre)%>%
  select(-word)%>%
  mutate(sum_genre_neg=sum(n))%>%
  ungroup()%>%
  select(genre,sum_genre_neg)%>%
  distinct()
sumsentiment_neg_genre

sumsentiment_pos_genre=wordsentiment_pos_genre%>%
  group_by(genre)%>%
  select(-word)%>%
  mutate(sum_genre_pos=sum(n))%>%
  ungroup()%>%
  select(genre,sum_genre_pos)%>%
   distinct()

genre_n=dt_lyrics%>%
  group_by(genre)%>%
  count()

sumsentiment_genre=sumsentiment_pos_genre%>%
  left_join(sumsentiment_neg_genre,by="genre")%>%
  left_join(genre_n,by="genre")

meansentiment_genre=sumsentiment_genre%>%
  mutate(mean_genre_pos=sum_genre_pos/n)%>%
  mutate(mean_genre_neg=sum_genre_neg/n)%>%
  select(-sum_genre_pos,-sum_genre_neg,-n)%>%
  filter(!genre=="Not Available")%>%
  filter(!genre=="Other")
meansentiment_genre
```

```{r warning=FALSE}
meansentiment_genre %>%
  pivot_longer(cols=c(mean_genre_pos,mean_genre_neg),names_to = "sentiment",values_to = "value")%>%
  group_by(sentiment) %>%
  top_n(10, value) %>%
  arrange(value) %>%
  ungroup() %>%
  mutate(genre = factor(genre, unique(genre))) %>%
  ungroup() %>%
  ggplot(aes(genre, value, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ sentiment, scales = "free", ncol = 2) +
  coord_flip() +
  labs(x = NULL, 
       y = "Median # of value containing each genre(positive/negative)")
```

Through the comparison of the two sets of histograms, we have an initial understanding of the emotional style of each genre: 

1. the positive emotional strength of pop music, country music, R & B and jazz is obviously greater than the negative emotional strength, so the style of these three songs should be positive.

2. The negative emotional strength of metal is more significant than the positive emotional strength, so the style of metal music should be negative.

3. we found that hip-hop is a music genre with a lot of emotions, and emotional words are common in lyrics. This is also consistent with our intuitive impression. Compared with folk songs, jazz music and other more narrative songs, hip hop music mainly expresses people's attitude.


As a master student in statistics , we try to perform statistical analysis and do correlation test

```{r warning=FALSE}
genre_word_df=tidy(corpus1) %>%
  select(id,text)%>%
  left_join(dt_lyrics,by="id")%>%
  select(id,genre,text)%>%
  unnest_tokens(word, text)%>%
  mutate(int=row_number())
test_genre=genre_word_df%>%
  inner_join(get_sentiments("bing"),by = "word")%>%
  filter(!genre=="Not Available")%>%
  filter(!genre=="Other")%>%
  mutate(genre=as.factor(genre))%>%
  mutate(sentiment=as.factor(sentiment))
test_genre
mytable1 <- xtabs(~sentiment+genre, data=test_genre) 
chisq.test(mytable1)
mytable1
```

At this time, sentiment and genre are both categorical variables. after Pearson's Chi-squared test,p-value < 2.2e-16. So it passed the correlation test. 

Thus the sentiment of the lyrics is related to genre.

```{r warning=FALSE}
total_sentiment_genre=meansentiment_genre%>%
  mutate(total=mean_genre_pos-mean_genre_neg)%>%
  select(genre,total)

total_sentiment_genre%>%
  ggplot(aes(genre, total, fill = genre)) +
  geom_col(show.legend = FALSE) +
  labs(x = "genre",y="total sentiment(positive/negative)")
```

we counted the emotions of songs in different genres. Observing the emotions that different genres convey to people under common circumstances, it is concluded that country, jazz, pop, and R&B are songs with highly positive sentiments. This is consistent with our preliminary guess earlier. Electronic and  folk music are songs with soft positive sentiments, rock and indie are songs with soft negative sentiments, while Hip-hop and metalare songs with strong negative sentiments. 

This is basically the same as how we feel when listening to music.When we're at a party, we often choose Jazz music, which represents carnival. When we are happy, we often choose pop, R&B or country music which conveys joy and relaxed emotions. When we are angry or feel pressure, we often choose hip-hop or metal music which often expresses sadness, anger, or helplessness emotion to resolve emotions.


```{r warning=FALSE}
genre_word_df=tidy(corpus1) %>%
  select(id,text)%>%
  left_join(dt_lyrics,by="id")%>%
  select(id,genre,text)%>%
  unnest_tokens(word, text)%>%
  mutate(int=row_number())
```

We also found that this was an overall effect. Take country music as an example. At the same time, there are 62051 positive words and 45704 negative words appear in all country songs in total. 


###3. sentimental changes in a  whole song among different genres.


With this in mind, and continuing to dig deeper into the sentiment of text, what we do next is: Analyze how sentiment showed by lyrics changes throughout the song by different genre(the time when their positive words and negative words appear),and draw a curve flow chart. We know that even if a few words are positive words, there are profound differences between them. In order to better reflect the level of emotion, we use the afinn dictionary for word and emotion correspondence at this time.

```{r warning=FALSE}
afinn_pos<-get_sentiments("afinn") %>% 
  filter(value>0)
afinn_neg<-get_sentiments("afinn") %>% 
  filter(value<0)

count_pos_genre<-genre_word_df%>% 
  inner_join(afinn_pos,by = "word")
count_neg_genre<-genre_word_df%>% 
  inner_join(afinn_neg,by = "word")

sort_genre=bind_rows(count_neg_genre,count_pos_genre)%>%
  group_by(genre)%>%
  mutate(number=as.integer(int))%>%
  ungroup()%>%
  select(-int)%>%
  mutate(id=as.integer(id))%>%
  arrange(id)
sum_word=word_df%>%
  mutate(id=as.integer(id))%>%
  count(id) %>% 
  mutate(csum = cumsum(n)) %>% 
  mutate(csum = c(0,csum[1:(length(csum)-1)]))
rate_genre=sort_genre%>%
  left_join(sum_word,by="id")%>%
  mutate(rate=(number-csum)/n)%>%
  select(genre,value,rate)
rate_genre
```


```{r warning=FALSE}
sequence_genre=rate_genre%>%
  mutate(number=row_number())%>%
  mutate(number=ifelse(rate<0.2,1,number))%>%
  mutate(number=ifelse(rate>=0.2&rate<0.4,2,number))%>%
  mutate(number=ifelse(rate>=0.4&rate<0.6,3,number))%>%
  mutate(number=ifelse(rate>=0.6&rate<0.8,4,number))%>%
   mutate(number=ifelse(rate>=0.8&rate<=1,5,number))
sequence_genre_group=sequence_genre%>%
  select(-rate)%>%
  group_by(genre,number)%>%
  summarise(mean= mean(value))%>%
  filter(!genre=="Not Available")%>%
  filter(!genre=="Other")
sequence_genre_group

```


```{r warning=FALSE}
sequence_genre_group%>%
  ggplot(aes(number,mean)) +
  geom_line() +
  facet_wrap(~genre, scales = "free", ncol = 3) +
  labs(x = NULL, 
       y = "Mean # of value on the track of time for each genre ")
```


In Figure , we can see how the plot of the song changes towards more positive or negative emotions on the track of time for each different genre.In other genres, emotions have climaxes and ups and downs. In particular, hip hop and metal have always been in negative emotions, and they have undergone a series of climax changes with the passage of song playback time.

To be specific:

1. We found that the emotional changes of country music, pop music, and R & B are very similar. They are all positive emotions, and this positive emotion gradually rises. From the previous histogram, we can also see that their overall positive emotion index is similar, about 2.5; This is basically in line with our concept. Take my own example. When I listen to a popular piece of music, my emotions usually rise gradually, and the lyricist will gradually increase the emotions in the words, such as joy or affection or emotion, from the original implicit expression to the last strong rendering. Finally, the listener may end with a lot of happiness and feel the great kindness of the world.

2. the mood of electronic music is generally on the rise, but there are fluctuations in the middle. This is similar to jazz and rock, but jazz is generally more emotional than electronic; rock is more negative than electronic. 

3. Folk music and hip-hop music are very similar in emotional ups and downs. At first, the mood of the entire song was higher, then it fell sharply, and then continued to climb. The difference is that hip-hop music reaches the lowest point, then stays, and then rises sharply to the highest point to end the music, but the folk music slowly falls back, and the final end is not the highest point of emotion, but the beginning is the most exciting moment of emotion. 

4. In general, except for the folk music, the mood of the songs is from low(less positive or more negative) to high(more positiver or less negative), and the ending is basically the highest, but the folk songs are the most positive at the beginning, as mentioned above.


###4. Contribution Analysis by affin

At this time, we use the afinn dictionary to analyze the contribution of positive affective words and negative affective words in the database.

```{r warning=FALSE}
contributions <- word_df%>%
  inner_join(get_sentiments("afinn"), by = "word") %>%
  group_by(word)%>%
  summarize(occurences = n(),
            contribution = sum(value))

contributions %>%
  top_n(25, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution, fill = contribution > 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip()
```

we can find the words with the greatest contributions to positive/negative sentiment values in the lyrics dataset.These words look generally reasonable as indicators of each genre/ages/song’s sentiment.

first, we can calculate each word’s contribution to each genre’s sentiment score, and visualize the strongest contributors from a selection of the groups.

```{r warning=FALSE}
contributions_genre=genre_word_df%>%
  inner_join(get_sentiments("afinn"), by = "word") %>%
  group_by(genre,word)%>%
  summarize(occurences = n(),
            contribution = sum(value))%>%
  filter(!genre=="Not Available")%>%
  filter(!genre=="Other")

contributions_genre %>%
  top_n(15, abs(contribution)) %>%
  mutate(word = reorder(word, contribution)) %>%
  ggplot(aes(word, contribution, fill = contribution > 0)) +
  geom_col(show.legend = FALSE) + 
  facet_wrap(~genre, scales = "free", ncol = 5) +
  coord_flip()
```

In the text analysis above, we first compared the similarities of the words in different songs. I found that the words a and b are very similar. For example, both like to use love,like, good, want,care to express joyful feelings and like to use pain, hell, alone, fuck to express sad feelings. Similarly, I found that and d have great similarities in terms. For example, they both like to use love, yeah, want to express joyful feelings, and like to use .alone, fuck, bad to express sad feelings.

To be specific:

1.  Country music and folk songs, as well as R & B music are similar in terms of words, that is to say, the words are relatively subtle, often using such as yeah, sweet, better, want to express joy, while using alone, no, kill, lost to express sadness.

2.  Jazz and pop music are more direct. For example, they express joy in direct words such as happy.

3. Rock music and electronic music are similar, and their word maps as above are very similar.

4. Hip hop music and indie are very similar in terms of words , because they often use shit, niggas, shit, bitch, expressed dissatisfaction with rude words. 

5. Metal as the main expression of negative emotion music, sadness or dissatisfaction with many words, such as pain, hate, fuck, death, fear and so on. In addition, the lyrics often contain fire, giving a very strong psychological impact. 

6.	Generally speaking, lyrics are often used in love, like to express positive emotions, and no to directly express negative emotions.

Therefore, as we can image, the music genres are connected to sentiments in lyrics.

###5.The position of words with larger sentimental contributions 

Based on this, we naturally asked a question: since the sentiment of the lyrics is related to words, is it that most frequently used positive-words like "love","like","want","good","happy" appear more at the end, and most commonly used negative-words like "wrong","no","alone","bad","lost", in What more appears at the beginning or middle? So, I will explore where these words appear in different genres.

```{r warning=FALSE}
s0=sort_genre%>%
  left_join(sum_word,by="id")%>%
  mutate(rate=(number-csum)/n)%>%
  select(word,genre,value,rate)%>%
  filter(word==c("love","like","want","good","happy","wrong","no","alone","bad","lost"))%>%
  mutate(number=row_number())%>%
  mutate(number=ifelse(rate<0.2,1,number))%>%
  mutate(number=ifelse(rate>=0.2&rate<0.4,2,number))%>%
  mutate(number=ifelse(rate>=0.4&rate<0.6,3,number))%>%
  mutate(number=ifelse(rate>=0.6&rate<0.8,4,number))%>%
   mutate(number=ifelse(rate>=0.8&rate<=1,5,number))%>%
  mutate(senti=ifelse(value>0,"positive","negative"))%>%
  filter(!genre=="NA")%>%
  filter(!genre=="Not Available")%>%
  filter(!genre=="Other")%>%
  select(-value,-rate)%>%
  group_by(genre,word,number,senti)%>%
  count()%>%
  ungroup()%>%
  group_by(genre,word)
s0
s1=s0%>%
  group_by(genre,word)%>%
  filter(n==max(n))%>%
  mutate(number=ifelse(n==n,mean(number),number))%>%
  distinct()
s1
```

```{r warning=FALSE}
s1%>%
  ggplot(aes(word,number,fill=senti)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~genre, scales = "free", ncol = 4) +
  labs(x = NULL, 
       y = NULL)+
  coord_flip()
```

1. From the figure we can find that in country music, the words love and good are mostly used in the fifth paragraph, and because of their high positive emotional score, the final mood of country music is very high. In general, positive words such as want, happy, etc. often appear in the middle to the final stage. At the same time, the middle part is accompanied by negative words such as no, bad, lost, making the emotions not very positive in this stage.

 
2. In electronic music, at the beginning, positive words prevailed (the green part is the main part from 0 to 2. Later, negative words were gradually added, which led to emotional depression. In addition, although both love and lost appeared more often in at the end of the song, because in the direction of their emotions, love expresses deeper than lost, thus suppressing negative emotions, so the emotions gradually rise again.

3. The meaning of folk music is not very consistent with the result of our previous song images.Since the first paragraph does not include the vocabulary we have chosen, we suspect that this may be because the way of expressing positive emotions in folk music is more peaceful. For example, it often uses the words "dear" and "miss", but they are not included in the range we have selected. In addition, it can be clearly felt that after the second paragraph, the mood of folk music fluctuates in a gentle trend within a low positive emotion.


4. Hip-hop, indie and jazz music are kind of similar. Both positive words and negative words coexist at the beginning. Later, words gradually decrease. After the fourth part, very strong positive words such as love are added, thus making emotions rise.

5. The charts of Pop and R & B are also very similar, which is consistent with the result of our previous song images.And the overall positive emotions are gradually rising.

6. Rock music is a bit weird. We found that the common emotional words like wrong, want, no, love, happy, good, bad, and alone appear almost at the very end. This is also logical. Generally speaking, the emotion of rock music is from light to strong, and the emotion is released as the song continues.

###6.sentimental changes in different ages 

First we examine the correlation between emotion and age

```{r warning=FALSE}
genre_n_selected = genre_n%>%
  filter(!genre=="Not Available"&!genre=="Other")

dt_lyrics_ages<-dt_lyrics%>%
  filter(year>=1970)%>%
  mutate(ages=row_number())%>%
  mutate(ages=ifelse(year<1980,"1970s",ages))%>%
  mutate(ages=ifelse(year>=1980,"1980s",ages))%>%
  mutate(ages=ifelse(year>=1990,"1990s",ages))%>%
  mutate(ages=ifelse(year>=2000,"2000s",ages))%>%
  mutate(ages=ifelse(year>=2010,"2010s",ages))
dt_lyrics_ages

corpus_ages<- VCorpus(VectorSource(dt_lyrics_ages$lyrics))
#create a tidy data structure
word_text_ages<- tidy(corpus_ages) %>%
  select(id,text)
#break the text into individual tokens
ages_genre_word_df=word_text_ages%>%
  left_join(dt_lyrics_ages,by="id")%>%
  select(genre,text,ages)%>%
  filter(!genre=="Not Available"&!genre=="Other")%>%
  unnest_tokens(word, text)
ages_genre_word_df
```


```{r warning=FALSE}
test_genre=ages_genre_word_df%>%
  inner_join(get_sentiments("bing"),by = "word")%>%
  filter(!genre=="Not Available")%>%
  filter(!genre=="Other")%>%
  mutate(ages=as.factor(ages))%>%
  mutate(sentiment=as.factor(sentiment))
test_genre
mytable2 <- xtabs(~sentiment+ages, data=test_genre) 
chisq.test(mytable2)
mytable2
```

At this time, sentiment and ages are both categorical variables. after Pearson's Chi-squared test,p-value < 2.2e-16, passed statistical correlation testThus the sentiment of the lyrics is related to ages.


###(1).among different genre

```{r warning=FALSE}
count_pos_ages_genre<-ages_genre_word_df%>% 
  inner_join(afinn_pos,by = "word")
count_neg_ages_genre<-ages_genre_word_df%>% 
  inner_join(afinn_neg,by = "word")
sort_ages_genre=bind_rows(count_neg_ages_genre,count_pos_ages_genre)%>%
  group_by(genre,ages)%>%
  summarise(sum=sum(value),
            mean=mean(value))%>%
  filter(!genre=="NA")%>%
  ungroup()

sort_ages_genre%>%
  ggplot(aes(ages,mean,fill=genre)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~genre, scales = "free", ncol = 2) +
  labs(x = NULL, 
       y = "Mean # of sentiment value(positive/negative)")
```

We visualized the emotional changes of different genres over time. From this we find that the emotions expressed by the same genre are also changing with the development of the times and social changes. 

To be specific:

1.  The music of the three genres of country, electronic, and rock experienced a great emotional decline in the 1980s (even from positive emotions to negative emotions). We suspect that the 1980s may be under the influence of a certain genre The remaining genres were reformed. But in the following 90's, emotions gradually rose(in positive direction). We speculate that this change may be due to the prevalence and decline of style over time. country，

2.  The sentimental changes in jazz and pop music have always been relatively stable, and both have remained at a high level of positive emotions. 

3.  Indie music has not appeared before, so we think that this genre of music genre may not appear until 2000. And its mood is gradually high-profile. 

4.	The mood of folk music basically reached its climax in the 1990s, but then gradually fell back and became more moderate. 


Next, we can also divide the total emotion (no genre division) according to different ages, so as to observe the influence of the era on the emotion of the lyrics.


###(2). no genre division

```{r warning=FALSE}
ages_word_df=word_text_ages%>%
  left_join(dt_lyrics_ages,by="id")%>%
  select(text,ages)%>%
  unnest_tokens(word, text)

count_pos_ages<-ages_word_df%>% 
  inner_join(afinn_pos,by = "word")
count_neg_ages<-ages_word_df%>% 
  inner_join(afinn_neg,by = "word")

sort_ages=bind_rows(count_neg_ages,count_pos_ages)%>%
  group_by(ages)%>%
  summarise(sum=sum(value),
            mean=mean(value))%>%
  filter(!ages=="NA")%>%
  ungroup()
sort_ages
```

```{r warning=FALSE}
sort_ages%>%
  ggplot(aes(ages,mean,fill=ages)) +
  geom_col(show.legend = FALSE)+
  labs(x = NULL, 
       y = "Mean # of sentiment value(positive/negative)")
```

For music of different ages, sentiments are also different.

With the passage of time, the overall positive emotions of the song gradually weaken, but at the same time, there will be small fluctuations with what happens around the world. Such as the economic depression of the country and so on, will affect the composition of songs. 

But in general, living a peaceful life and better and better economic development, people will focus more on their negative emotions, and also people's appreciation of music and their tolerance will increase. Songs that express negative emotions are accepted by people. At the same time, with the rapid development of the times, people's life pressures increase, more negative songs are needed to release anger or sadness, and people have more courage to express their singing.




